---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bizwiz

<!-- badges: start -->
<!-- badges: end -->

This package was designed with the intention of making it easy to generate fake business data to work with in R. 
The functions in this package allow the user to quickly make dataframes with randomly generated names, salaries, company revenue, and expenses. 
I hope that you enjoy using the bizwiz package and that it streamlines your work.

## Installation

You can install the development version from [GitHub](https://github.com/conant2/bizwiz) with:

``` r
# install.packages("devtools")
devtools::install_github("conant2/bizwiz")
```
## Examples

bizstaff gives a dataframe of employees with variables: employeeID (unique employee IDs), GivenName (first, or given name), Surname (last name), 
income (the income of the employee), yearsemployed (number of years the employee has worked), Position (the job title of the employee). 
```{r example}
library(bizwiz)
# A staff data frame example
bizstaff(10)
```

bizcompany gives a dataframe of company branches with variables: branchID (unique branch IDs), revenue (the revenue for the branch), expenses (the expenses for the branch), profit (the difference between revenue and expenses), units_sold (the number of items sold for the branch). 
```{r}
library(bizwiz)
# A company data frame example
bizcompany(10)
```

