---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bizwiz

<!-- badges: start -->
<!-- badges: end -->

This package was designed with the intention of making it easy to generate fake business data to work with in R. 
             The functions in this package allow the user to quickly make dataframes with randomly generated names, salaries, company revenue, and expenses. 
             I hope that you enjoy using the bizwiz package and that it streamlines your work.

## Installation

You can install the released version of bizwiz from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bizwiz")
```

And the development version from [GitHub](https://github.com/conant2/bizwiz) with:

``` r
# install.packages("devtools")
devtools::install_github("conant2/bizwiz")
```
## Examples


```{r example}
library(bizwiz)
# A staff data frame example
bizstaff(10)
```

```{r}
library(bizwiz)
# A company data frame example
bizcompany(10)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

